Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-24 ms.qmd
Fixed table issues. Was a yaml problem

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: true
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-labels: "Table"
---

>>>>

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: true
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---
